

---
title: "Lab_3"
author: "P-Hackers"
date: "9/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)
```

## Team Lab Report
<p>&nbsp;</p>
### Overall Question
  How does smoking affect weight? 
  
### Why Important?
  The question is important because it will show what effects smoking has on human beings. 
  
  
### More Detailed Why Important
  Showing what effect smoking has on someone’s weight may deter or encourage people to smoke. This is important because it could impact the cigarette industry. If the data shows that generally smokers weigh more than non-smokers, then less people will smoke. If the data shows that generally smokers weigh less than non-smokers, then more people will smoke. 
  
  
### Plot
```{r, echo=FALSE, message=FALSE, warning=FALSE}
P_names <- c(
  '0' = "Non-Smoker",
  '1' = "Smoker",
  'm' = "Male",
  'f' = "Female"
)
ggplot(data=cdc, mapping = aes(x = weight)) +
  geom_histogram() +
  facet_wrap(gender~smoke100,labeller= as_labeller(P_names))+
  labs(title = "The Gender-Inclusive Study of Weight vs Smoking", x = 'Weight',y = 'Study Count') +
  theme_bw()+
  theme(plot.title = element_text(color = "blue", face = "bold"))
```
 
  
### Conclusion
  We found that most respondents were between 100 and 200 pounds. However, smokers are typically slightly higher in weight than non-smokers. This shows that smoking has some effect on a person's weight however, the difference is very minimal. 
  
### Recommendation
Due to the little correlation between smoking and weight, we suggest that the Center for Disease Control and Prevention does not use weight as a factor for why individuals should stop smoking. The CDC should, instead, study the relationship between smoking and overall health because there will be a higher correlation between those two things. However, the CDC should make the public aware of the slight weight increase due to smoking. Additionally, the CDC should further look into why more average weight respondents smoked. There could be a correlation between average weight, smoking, and a third factor, like stress levels. 
  
## Individual Reports:
<p>&nbsp;</p>

**Julia Foley**

```{r, echo=TRUE, message=FALSE, warning=FALSE}

ggplot(data = cdc,mapping = aes(y = exerany,x = age, color = gender)) +
  geom_col() +
  theme_bw()
```

##### Findings:
  When comparing age and exercise, I found that respondents who were younger exercised more than respondents who were older. The data shows a steady decline in the number of respondents, years 38 to 100, who have exercised in the last month. Additionally, Men exercise significantly more than women. However, women, years 95 to 100, exercise more than men. Overall, as age increases, the amount of exercise decreases. 
  
<p>&nbsp;</p>

#### **Declan Franklin**

##### Hypothesis:

Individuals that smoke will have a lower quality of health, but they will weigh less than the Non-Smokers.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
smoke_names <- c(
  '0' = "Non-Smoker",
  '1' = "Smoker"
)
ggplot(data = cdc,mapping = aes(x = weight, y = genhlth )) +
  geom_smooth(method=lm, se=FALSE) +
  stat_boxplot()+
  facet_wrap(~smoke100, labeller= as_labeller(smoke_names)) +
  labs(title = "The Impact of Smoking on Weight vs General Health", caption ="The black-lines represent the average of each data set",x = 'Weight',y = 'General Health') +
  theme_dark()+
  theme(plot.caption = element_text(color = "black", face = "bold.italic"), plot.title = element_text(color = "blue", face = "bold"))
 
```

##### Findings and Conclussions:

After running the numbers, the data showed that my hypothesis was incorrect. In general, the smokers hold a higher quality of general health and their weight fluctuates. The Non-Smokers weight gets heavier as the quality of health goes from excellent to poor. In conclusion, the fact that the smokers knew that they smoke at the time of the survey was most likely a threat to the validity of the experiment.

<p>&nbsp;</p>

#### **Andres Acevedo**

 ```{r,echo=FALSE, message=FALSE, warning=FALSE}
 ggplot(data = cdc) +
  geom_bar(mapping = aes(x = genhlth, fill = gender), position = "dodge") + facet_grid(exerany~smoke100)
  ```


## What Each Team Member Did

<p>&nbsp;</p>

#### **Julia Foley**

##### Individual:
   I, Julia Foley, compared the amount of exercise with age and gender using a plot I created on R Markdown. I created a plot by using ggplot, color=gender, geom_col, and theme_bw. All of these codes made it easier for the reader to interpret and understand the data. Then, I studied my findings and reported it in the findings section of my report. 
   
##### Team:
  My team role was to do the writing for the Report. I created the outline of the document and created a file. I, then, wrote the why important and more detailed why important sections. Additionally, I wrote the conclusion and recommendation sections of the Lab Report. It was interesting to analyze the data and see the relationship between weight and smoking. 
  
<p>&nbsp;</p>  

#### **Declan Franklin**
##### Individual:
  I used ggplot to test my hypothesis that studies the impact of smoking on weight and general health. I created a plot using geom_smooth to graph weight vs general health. I used stat_boxplot to see the average score, and I used a facet_wrap to have graphs of smokers vs non smokers. The data was pretty interesting, and proved my hypothesis incorrect.

##### Team:     
 My team role was to help with the syntax and apperence of our markdown. My goal is to make the finished piece look nice and for it to run effectivly.  

<p>&nbsp;</p>

## Nisia Pinto 
**Individual:**
Plot relationship between exercise and general health in men and women.
I created a ggplot and confirmed my hypothesis that men and women with better health have exercise equally.

```{r}
ggplot(data = cdc, mapping = aes (x=gender,y=exerany,color=genhlth))+ geom_col(se=FALSE) + facet_wrap(~ genhlth, nrow = 2)
```
These five plots represent the general health of men and women according to the number of times they exercise.In this data, men exercise more than women.There is a small difference between cases. As health quality increases more men and women exercise. With fair health, men tend to exercise more than women.

**Team:**
